---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Roboto+Serif&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Raleway&display=swap');

body {
      background-color: ##e6e6fa
}

h2 {
  font-family: "Raleway";
  font-weight: 700;
  font-size: 30px;
  color: #080808;
}

p {
   font-family: 'Roboto';
   font-size: 15px;
   width: 80%
   font-weight: 200
}
```

```{r, echo=FALSE}
library(tidyverse)
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSHm7BhfFMlG1Jn-p4xgNdRKFy8_2MEfX-v6xtUSz7tgvtypTbBVit7zaWk_f_cVnamirMYafGvn1E0/pub?gid=921568506&single=true&output=csv")
logged_data <- rename(logged_data, time_recorded = 1, day_of_week = 2, time_of_day = 3,
                      trip_duration = 4, aqua_seen = 5, aqua_number = 6, 
                      car_colours = 7)
logged_data$trip_duration <- as.numeric(logged_data$trip_duration)/60
```


## Day of the Week and Toyota Aquas

Does the day of the week influence the rate of Toyota Aquas that are spotted? Participants of the survey kept track of the number of Toyota Aquas they spotted while driving and recorded the duration of their trip.

```{r, echo=FALSE}
logged_data$day_of_week <- factor(logged_data$day_of_week, levels = 
                                    c("Monday", "Tuesday", "Wednesday",
                                      "Thursday", "Friday", "Saturday",
                                      "Sunday"))

ggplot(data = logged_data) +
    geom_bar(aes(x = day_of_week, fill = day_of_week)) +
    labs(title = "Aqua Spotting Days",
         subtitle = "The days of the week that were our observations made",
         caption = "Source: Survey collected by André Leader, Statistics Undergrad at UoA",
         x = "Day Measured",
         y = "Count") +
     theme(legend.position = "none")
```

The above barplot counts the amount of observations (trips in the car) that were made on each day of the week. Although our sample size is very limited, we have data for each day of the week and can comment on hour our data differs based on the day.

By dividing the number of Aquas spotted by the duration of each trip, the rate of Aquas spotted per minute for each trip was calculated.

```{r, echo=FALSE}
logged_data <- cbind(logged_data, 
                     aqua_rate = logged_data$aqua_number/logged_data$trip_duration)

# The total average rate of aquas per minute, and for each day of the week,
# alongside the day with the maximum rate
avg_aqua_rate <- round(mean(logged_data$aqua_rate, na.rm=TRUE),2)
avg_rate_mon <- mean(logged_data$aqua_rate[logged_data$day_of_week=="Monday"], na.rm=TRUE)
avg_rate_tue <- mean(logged_data$aqua_rate[logged_data$day_of_week=="Tuesday"], na.rm=TRUE)
avg_rate_wed <- mean(logged_data$aqua_rate[logged_data$day_of_week=="Wednesday"], na.rm=TRUE)
avg_rate_thu <- mean(logged_data$aqua_rate[logged_data$day_of_week=="Thursday"], na.rm=TRUE)
avg_rate_fri <- mean(logged_data$aqua_rate[logged_data$day_of_week=="Friday"], na.rm=TRUE)
avg_rate_sat <- mean(logged_data$aqua_rate[logged_data$day_of_week=="Saturday"], na.rm=TRUE)
avg_rate_sun <- mean(logged_data$aqua_rate[logged_data$day_of_week=="Sunday"], na.rm=TRUE)
avg_week <- c(avg_rate_mon, avg_rate_tue, avg_rate_wed, avg_rate_thu, 
              avg_rate_fri, avg_rate_sat, avg_rate_sun)
days <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday","Sunday")
max_day <- days[which.max(avg_week)]
max_day_num <- avg_week[which.max(avg_week)]
```

The average rate of Toyota Aquas spotted across the study was **`r avg_aqua_rate` Aquas per minute.**

The day with the highest rate was **`r days[which.max(avg_week)]`** with an average rate of **`r round(max_day_num,2)` Aquas per minute**.

Our sample size was very small, and so we cannot claim with certainty that **`r days[which.max(avg_week)]`** tends to show the highest number of Toyota Aquas on the road. However, based on our sample data, Toyota Aquas were spotted more frequently on **`r max_day`** on average. It would be worth testing the statistical significance of the difference between the **`r max_day`** average (**`r round(max_day_num,2)`**) and the mean average rate (**`r avg_aqua_rate`**) of Aquas per minute.

## Toyota Aqua Colours

Survey participants also recorded what car colours they encountered during their observations. Below is a plot displaying the number of observations in which each colour of Toyota Aqua were spotted. The bars are colour coded to match the car colour represented.

```{r}
# Adds multiple rows for each observation, solely to remove multiple car colours
# from being in the same cell
data_longer <- logged_data %>%
    separate_rows(car_colours, sep = ", ")

#Removes the row that saw no Aquas
data_longer_cars <- data_longer[data_longer$aqua_seen=="Yes",]

# This converts our car_colours vector to a factor that we can use to determine 
# the order that our bars are plotted
data_longer_cars$car_colours <- factor(data_longer_cars$car_colours, 
                                       levels = unique(data_longer_cars$car_colours))

# This determines colours for the "silver" and "other" levels of car_colours,
# as these colours do not prexist in R
bar_colours <- as.character(unique(data_longer_cars$car_colours))
bar_colours[2] <- "lightgrey"
bar_colours[5] <- "gray28"

# This gets the colours to use for each bar to align with the levels of our 
# car_colours factor
colour_map <- setNames(bar_colours, levels(data_longer_cars$car_colours))

# We must use the scale_fill_manual function to determine to draw upon our
# assigned order of bar colours
ggplot(data = data_longer_cars) +
    geom_bar(aes(x = car_colours, fill = car_colours)) +
    scale_fill_manual(values = colour_map) +
    labs(title = "Spotted Colours",
         subtitle = "The number observations that each colour Aqua was in?",
         caption = "Source: Survey collected by André Leader, Statistics Undergrad at UoA",
         x = "Toyota Aqua Colour",
         y = "Number of trips the colour was spotted on") +
         theme(legend.position = "none")

# This code determines the name of the factor level with the greatest number of 
# entries, and the number of these entries
main_colour <- names(which.max(table(data_longer_cars$car_colours)))
main_colour_num <- max(table(data_longer_cars$car_colours))
```

The Toyota Aqua colour spotted in the most observations was **`r main_colour`** which was spotted in **`r main_colour_num`** trips. This suggests that you are most likely to encounter a **`r main_colour`** Toyota Aqua when driving.
